Cannibalism among the supermassive black holes

### 2018-05-18 paper.tex
More modifications

\subsection{Overview of simulation}
Our simulations focused on elliptical galaxies with central SMBHs. The galaxies were given a background potential based on the Ostriker-Stone profile (\citet{2015ApJ...806L..28S}), which is a three-parameter potential-density pair, whose quantities such as density, potential, and binding energy can be written in closed form.  The galaxies were evolved between $0 < z < 4$.  Orbiting black holes were periodically introduced into the "host" galaxy and their dynamical interaction with the background potential and central SMBH were followed, as described further below.

@@

\subsection{Merger tree}
Our merger tree data came from two sources:
\begin{itemize}
\item Galactic merger tree data from simulations of \citet{2012MNRAS.425..641L} (hereafter Lackner12), which was centered on galaxies at each redshift slice, providing information on the galaxies' stellar mass, dark matter mass, central BH, and any orbiting black holes within the galaxy.
\item SMBH evolution simulations of \citet{2015ApJ...799..178K} (hereafter Kulier15), which used the large-scale hydrodynamical galaxy simulations outlined in \citet{2011ApJ...741...99C, 2011ApJ...742L..33C, 2012ApJ...753...17C, 2012ApJ...748..121C, 2013ApJ...770..139C}.  The data was centered around SMBHs at each redshift slice between $0 < z < 4$, giving information for each SMBH's seed mass, accreted and seed mass, its host galaxy (categorically defined), the stellar mass in its host galaxy, and time after z=4 at which the BH entered the host galaxy (if it is not the central BH).
\end{itemize}

@@

The merger tree data from Lackner12 and Kulier15 provided 1,830 galaxies in total.  However, not all the galaxies were useful for our simulations.  We placed further:
\begin{itemize}
\item The galaxies had to exist through the entire simulation ($0 < z < 4$).
\item They had to have a central SMBH.
\item We ordered the galaxies by decreasing mass at $z=0$, and starting with the largest tier of mass (~$10^{14} M_{\odot}$), we spaced their masses by approximately 1-2 orders of magnitude.  We chose the four largest galaxies that also satisfied the above criteria.
\end{itemize}

@@

Lackner12 noted that the efficiency of star formation in their simulations, defined as $f_*=M_*/M_{DM}(\Omega_{DM}/\Omega_b)$, was approximately 0.6.  Compared with the expected range of $0.10 \lessapprox f_* \lessapprox 0.15$ that they referenced from \citet{2012ApJ...746...95L}, their stellar masses were a factor of roughly 4 times greater.  In order to adjust our stellar masses to levels more in line with current observations, we used observational data from \citet{2018AstL...44....8K}, in particular Figure 11. (SHOULD I ADD PLOT OF OUR ORIGINAL STELLAR DATA?  THE PLOT FROM KRAVTSOV WAS RECREATED BY EYEBALL WITH A FEW STRAIGHT LINES TO APPROXIMATE HIS CURVE.  HOW TO INCORPORATE THAT?)

>>>>

\subsection{Overview of simulation}
Our simulations focused on elliptical galaxies with central SMBHs. The galaxies were given a background potential based on the Ostriker-Stone profile (\citet{2015ApJ...806L..28S}), which is a three-parameter potential-density pair, whose quantities such as density, potential, and binding energy can be written in closed form.  The galaxies were evolved from $4 > z > 0$.  Orbiting black holes were periodically introduced into the "host" galaxy and their dynamical interaction with the background potential and central SMBH were followed, as described further below.

@@

\subsection{Merger tree}
Our merger tree data came from two sources:
\begin{itemize}
\item Galactic merger tree data from simulations of \citet{2012MNRAS.425..641L} (hereafter Lackner12), which was centered on galaxies at each redshift slice, providing information on the galaxies' stellar mass, dark matter mass, central BH, and any orbiting black holes within the galaxy.
\item SMBH evolution simulations of \citet{2015ApJ...799..178K} (hereafter Kulier15), which used the large-scale hydrodynamical galaxy simulations outlined in \citet{2011ApJ...741...99C, 2011ApJ...742L..33C, 2012ApJ...753...17C, 2012ApJ...748..121C, 2013ApJ...770..139C}.  The data was centered around SMBHs at each redshift slice from $4 > z > 0$, giving information for each SMBH's seed mass, accreted and seed mass, its host galaxy (categorically defined), the stellar mass in its host galaxy, and time after z=4 at which the BH entered the host galaxy (if it is not the central BH).
\end{itemize}

@@

The merger tree data from Lackner12 and Kulier15 provided 1,830 galaxies in total.  However, not all the galaxies were suitable for our simulations.  We placed further requirements as follows:
\begin{itemize}
\item The galaxies had to exist through the entire simulation ($4 > z > 0$).  If they merged with other galaxies, they had to have been the "surviving" galaxy at each merger.
\item They had to have accumulated orbiting black holes by z = 0.
\end{itemize}

The Kulier15 merger tree collected black holes entering galaxies during the simulation and noted the time after z=4 at which they entered their host galaxy.  Nothing further was done with them, so each galaxy had a "running list" of other galaxies/BHs orbiting them at z=0.  Clean up this paragraph.

@@

\subsubsection{Galactic Stellar Mass Adjustment}
Lackner12 noted that the efficiency of star formation in their simulations, defined as $f_*=M_*/M_{DM}(\Omega_{DM}/\Omega_b)$, was approximately 0.6.  Compared with the expected range of $0.10 \lessapprox f_* \lessapprox 0.15$ that they referenced from \citet{2012ApJ...746...95L}, their stellar masses were a factor of roughly 4 times greater.  In order to adjust our stellar masses to levels more in line with current observations, we used observational data from \citet{2018AstL...44....8K}, in particular Figure 11.
\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/stellar_to_halo_ratio.png}
\caption{Original and rescaled stellar masses}
\label{fig:stellar1}
\end{center}
\end{figure}
